Demonstration of matching route networks

### 2024-01-29 r/README.qmd

```{r}
m = mapview::mapview(princes_street_minimal)
princes_street_minimal_x = mapedit::editMap(m)
names(princes_street_minimal_x)
princes_street_minimal_x_1 = princes_street_minimal_x$drawn
princes_street_minimal_x_1 = princes_street_minimal_x_1 |>
  transmute(id = 1:n())
```

```{r}
bind_rows(
  princes_street_minimal |>
    transmute(layer = "y"),
  princes_street_minimal_x_1 |>
    transmute(layer = "x")
) |>
  plot(lwd = 5)
```

```{r}
dir.create("data-raw")
dir.create("data-raw/geojson")
sf::write_sf(princes_street_minimal, "data-raw/geojson/princes_street_minimal.geojson")
sf::write_sf(princes_street_minimal_x_1, "data-raw/geojson/princes_street_minimal_x_1.geojson")
```

>>>>

```{r}
#| eval: false
m = mapview::mapview(princes_street_minimal)
princes_street_minimal_x = mapedit::editMap(m)
names(princes_street_minimal_x)
princes_street_minimal_x_1 = princes_street_minimal_x$drawn
princes_street_minimal_x_1 = princes_street_minimal_x_1 |>
  transmute(id = 1:n())
```

```{r}
#| echo: false
#| eval: false
princes_street_minimal_x_1_points = sf::st_cast(princes_street_minimal_x_1, "POINT")
princes_street_minimal_x_1_point_buffers = sf::st_buffer(princes_street_minimal_x_1_points, 5) |>
  sf::st_union()
plot(princes_street_minimal_x_1_point_buffers)
plot(princes_street_minimal_x_1, add = TRUE)
```

```{r}
princes_street_minimal_x_1 = sf::st_difference(princes_street_minimal_x_1, princes_street_minimal_x_1_point_buffers)
```

```{r}
bind_rows(
  princes_street_minimal |>
    transmute(value = as.character(value)),
  princes_street_minimal_x_1 |>
    transmute(value = "x")
) |>
  plot(lwd = 5)
```

```{r}
dir.create("data-raw")
dir.create("data-raw/geojson")
sf::write_sf(princes_street_minimal, "data-raw/geojson/princes_street_minimal.geojson", delete_dsn = TRUE)
sf::write_sf(princes_street_minimal_x_1, "data-raw/geojson/princes_street_minimal_x_1.geojson", delete_dsn = TRUE)
```
